Mirror, mirror on the wall. Who's the best match of them all?

### 2023-11-22 PNAS/index.Rnw
Fix yaxis label

\firstpage[3]{8}
% Use \firstpage to indicate which paragraph and line will start the second page and subsequent formatting. In this example, there are a total of 11 paragraphs on the first page, counting the first level heading as a paragraph. The value {12} represents the number of the paragraph starting the second page. If a paragraph runs over onto the second page, include a bracket with the paragraph line number starting the second page, followed by the paragraph number in curly brackets, e.g. "\firstpage[4]{11}".

@@

studies <- tibble(single_rmp = c( 0.004545,0.00704, 0.0724), study = c("Best (2022)","Bajic (2020)",  "Mattijssen (2021)"), y = c(-0.025, .15, 0.6), hjust = c(0, 0, 1))
ggplot(res, aes(x = single_rmp, y = overall, group = factor(N), color = factor(N))) +
  geom_line() +
  coord_cartesian(xlim = c(0, 0.07), ylim = c(0, 1)) +
  ylab("Probability of a coincidental match (N comparisons)") +
  xlab("Probability of a false positive (1 comparison)") +
  scale_y_continuous(breaks = seq(0, 1, .1), minor_breaks = seq(0, 1, .05)) +
  ggtitle("Wire Comparison: Controlling Overall False Positive Rate") +
  geom_vline(xintercept = 0.02, linetype = "dashed", color = "grey40") +
  geom_vline(xintercept = studies$single_rmp, linetype = "51", color = "grey50") +
  geom_label(data = studies[1,], aes(x = single_rmp, y = y, label = study), inherit.aes = F, hjust = studies$hjust[1], vjust = 0) +
  geom_label(data = studies[2,], aes(x = single_rmp, y = y, label = study), inherit.aes = F, hjust = studies$hjust[2], vjust = 0) +
  geom_label(data = studies[3,], aes(x = single_rmp, y = y, label = study), inherit.aes = F, hjust = studies$hjust[3], vjust = 0) +
  annotate(geom = "label", x = 0.02, y = 0.1, label = "Pooled error rate \nused in this paper", color = "grey40", hjust=0) +
  scale_color_discrete("# comparisons") +
  theme_bw() +
  theme(legend.position = c(1, 0), legend.justification = c(1, 0), legend.background = element_rect(color = "black"))
@

>>>>

\firstpage[4]{7}
% Use \firstpage to indicate which paragraph and line will start the second page and subsequent formatting. In this example, there are a total of 11 paragraphs on the first page, counting the first level heading as a paragraph. The value {12} represents the number of the paragraph starting the second page. If a paragraph runs over onto the second page, include a bracket with the paragraph line number starting the second page, followed by the paragraph number in curly brackets, e.g. "\firstpage[4]{11}".

@@

studies <- tibble(single_rmp = c( 0.004545,0.00704, 0.0724), study = c("Best (2022)","Bajic (2020)",  "Mattijssen (2021)"), y = c(-0.025, .15, 0.6), hjust = c(0, 0, 1))
ggplot(res, aes(x = single_rmp, y = overall, group = factor(N), color = factor(N))) +
  geom_line() +
  coord_cartesian(xlim = c(0, 0.07), ylim = c(0, 1)) +
  ylab("Probability of a false positive (N comparisons)") +
  xlab("Probability of a false positive (1 comparison)") +
  scale_y_continuous(breaks = seq(0, 1, .1), minor_breaks = seq(0, 1, .05)) +
  ggtitle("Wire Comparison: Controlling Overall False Positive Rate") +
  geom_vline(xintercept = 0.02, linetype = "dashed", color = "grey40") +
  geom_vline(xintercept = studies$single_rmp, linetype = "51", color = "grey50") +
  geom_label(data = studies[1,], aes(x = single_rmp, y = y, label = study), inherit.aes = F, hjust = studies$hjust[1], vjust = 0) +
  geom_label(data = studies[2,], aes(x = single_rmp, y = y, label = study), inherit.aes = F, hjust = studies$hjust[2], vjust = 0) +
  geom_label(data = studies[3,], aes(x = single_rmp, y = y, label = study), inherit.aes = F, hjust = studies$hjust[3], vjust = 0) +
  annotate(geom = "label", x = 0.02, y = 0.1, label = "Pooled error rate \nused in this paper", color = "grey40", hjust=0) +
  scale_color_discrete("# comparisons") +
  theme_bw() +
  theme(legend.position = c(1, 0), legend.justification = c(1, 0), legend.background = element_rect(color = "black"))
@
